--- 
title: "Computational studies on ageing and age-related diseases"
subtitle: ""
author: "Handan Melike Dönertaş"
degreedate: "April 2020"
description: ""
documentclass: unicam
fontsize: 12pt
papersize: a4
classoption: twosided
geometry: "left=37mm, right=30mm, top=35mm, bottom=30mm"
linestretch: 1.5
toc-depth: 2
lof: True
lot: True
crest: img/logo.jpg
mainfont: Helvetica
degreetitle: Philosophy of Science
college: Darwin College
dept: European Bioinformatics Institute (EMBL-EBI)
university: University of Cambridge
dedication: Anne ve anneanneme, her zaman yanımdaydılar ve bugün bu tezi yazabiliyor olmayı onlara borçluyum...
acknowledgements: |
  `r if(knitr:::is_latex_output()) paste(readLines("acknowledgements.txt"), collapse = '\n  ')`
declaration:  |
  `r if(knitr:::is_latex_output()) paste(readLines("declaration.txt"), collapse = '\n  ')`
abstract: | 
  `r if(knitr:::is_latex_output()) paste(readLines("abstract.txt"), collapse = '\n  ')`
site: bookdown::bookdown_site
bibliography: [thesis.bib, isildak2020.bib, donertas2020.bib, donertas2020si.bib, temreview.bib, intro.bib]
biblio-style: apa.csl
link-citations: yes
---

# Introduction

```{r include_packages, include = FALSE}
library(thesisdown)
library(knitr)
library(png)
library(kableExtra)
library(tidyverse)
library(ggthemes)
library(ggpubr)
```

```{r setupIndex, include=FALSE}
knitr::opts_chunk$set(echo = F, cache=T, message=F, warning=F, tidy=TRUE, 
                      tidy.opts=list(width.cutoff=55), fig.align = 'center')
```

<!-- makeindex thesis.nlo -s nomencl.ist -o thesis.nls -->

\nomenclature[A]{ROS}{Reactive Oxygen Species}
\nomenclature[A]{AP}{Antagonistic Pleiotropy Theory of Ageing}
\nomenclature[A]{MA}{Mutation Accumulation Theory of Ageing}
\nomenclature[A]{SASP}{Senescence-Associated Secretory Phenotype}
\nomenclature[A]{ITP}{NIA Interventions Testing Program}
\nomenclature[A]{DR}{Dietary Restriction}
\nomenclature[A]{NSN}{Nutrient-Sensing Network}
\nomenclature[A]{SVA}{Surrogate Variable Analysis}
\nomenclature[A]{IQR}{Interquartile Range}
\nomenclature[A]{GWAS}{Genome-Wide Association Study}
\nomenclature[A]{ARD}{Age-Related Disease}
\nomenclature[A]{ICD}{International Classification of Diseases}
\nomenclature[A]{HES}{Hospital Episode Statistics}
\nomenclature[A]{SR}{Self-Reported}
\nomenclature[A]{FDR}{False Discovery Rate}
\nomenclature[A]{SNP}{Single Nucleotide Polymorphisms}
\nomenclature[A]{eQTL}{Expression Quantitative Trait Loci}
\nomenclature[A]{PCA}{Principal Component Analysis}
\nomenclature[A]{MAF}{Minor Allele Frequency}
\nomenclature[A]{FDA}{U.S. Food and Drug Administration}
\nomenclature[A]{KS}{Kolmogorov–Smirnov}
\nomenclature[A]{NES}{Normalised Enrichment Score}
\nomenclature[A]{GSEA}{Gene Set Enrichment Analysis}
\nomenclature[A]{TF}{Transcription Factor}
\nomenclature[A]{PAM}{Partitioning Around Medoids}
\nomenclature[A]{CORT}{Temporal Correlation Coefficient}
\nomenclature[A]{MHC}{Major Histocompatibility Complex}
\nomenclature[A]{LD}{Linkage Disequilibrium}
\nomenclature[A]{LCV}{Latent Causal Variable}
\nomenclature[A]{GCP}{Genetic Causality Proportion}
\nomenclature[A]{BY}{Benjamini-Yekutieli}
<!-- \nomenclature[G]{mTOR}{Mammalian target of rapamycin} -->
<!-- \nomenclature[G]{TORC1}{mTOR Complex 1} -->
<!-- \nomenclature[G]{IGF-1}{Insulin-like growth factor 1} -->
<!-- \nomenclature[G]{AMPK}{AMP-activated protein kinase} -->
<!-- \nomenclature[G]{SIRT1}{Sirtuin 1} -->
<!-- \nomenclature[G]{CDKN2A}{Cyclin dependent kinase inhibitor 2A} -->
<!-- \nomenclature[G]{CDKN2B}{Cyclin dependent kinase inhibitor 2B} -->
<!-- \nomenclature[G]{APOE}{Apolipoprotein E } -->
<!-- \nomenclature[G]{FOXO}{Forkhead box protein O} -->
<!-- \nomenclature[G]{GPR137B}{G Protein-Coupled Receptor 137B} -->

\nomenclature[D]{UKBB}{UK Biobank}
\nomenclature[D]{GTEx}{Genotype-Tissue Expression}
\nomenclature[D]{GO BP}{Gene Ontology Biological Process}
\nomenclature[D]{GO MF}{Gene Ontology Molecular Function}
\nomenclature[D]{GO CC}{Gene Ontology Cellular Component}
\nomenclature[D]{DO}{Disease Ontology}
\nomenclature[D]{CMap}{Connectivity Map}


<!-- \nomenclature[H]{DVT  }{Deep Vein Thrombosis} -->
<!-- \nomenclature[H]{GORD }{Gastro-Oesophageal Reflux Disease} -->
<!-- \nomenclature[H]{ENT  }{Ears, Nose and Throat} -->

